### 2020-05-04 thesis_template/1_Intro/intro.tex
ready to review

Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce \cite{ApacheHadoopHomePage}, 
Apache Spark \cite{ApacheSparkHomePage}, and Apache Flink \cite{ApacheFlinkHomePage}. 
These tools have brought reliable and scalable ways to deal massive data. 
These has become widely popular, in which data-parallel computations are executed on clusters of unreliable machines by systems that automatically provide locality-aware scheduling, 
fault tolerance, and load balancing.

>>>>

Multiple cluster computing analysis tools have been developed, such as Hadoop MapReduce \cite{ApacheHadoopHomePage}, 
Apache Spark \cite{ApacheSparkHomePage}, and Apache Flink \cite{ApacheFlinkHomePage} \cite{DBLP:journals/debu/CarboneKEMHT15}. 
These tools have brought reliable and scalable ways to deal massive data. 
These has become widely popular, in which data-parallel computations are executed on clusters of unreliable machines by systems that automatically provide locality-aware scheduling, 
fault tolerance, and load balancing.

### 2020-05-04 thesis_template/2_RelatedWork/model/linalg.tex
ready to review

The original BLAS and LAPACK are written in Fortran90. Linear algebra library used for Spark is netlib-java, which is a Java wrapper library for Netlib, C API of BLAS and LAPACK. 
The reason why the developers addressed to use this package is that the BLAS and LAPACK are already bug free and implementing linear algebra library from scratch can usually buggy.

However, the main advantage of use of BLAS and LAPACK is system optimized implementation. So if we implement original Fortran linear algebra library, it cannot perform as well as BLAS and LAPACK. 
And the performance would not be such different from one of implementation in Java or Rust.  If we want to test only memory management between Rust and Java, 
it can be enough implementation of linear algebra operation from  pure Java and Rust sacrificing the best performance taking advantage of system optimization.

@@

Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
First, if we have installed machine optimised system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
instead of calling native libraries by using Java Native Interface (JNI).

@@

Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation. 
To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
while keeping vector operations local to the driver.

@@

ND4J has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.

>>>>

@@

Netlib-java is a Java wrapper of BLAS, LAPACK, and ARPACK. Netlib-java choose  implementation of linear algebra depending on installation of the libraries. 
First, if we have installed machine optimized system libraries, such as Intel MKL and OpenBLAS, netlib-java will use these as the implementation to use. 
Next, it try to load netlib references which netlib-java use CBLAS and LAPCKE interface to perform BLAS and LAPACK native call. 
The last option is to use f2j which is intended to translate the BLAS and LAPACK libraries from their Fortran77 reference source code to Java class files, 
instead of calling native libraries by using Java Native Interface (JNI).

@@

Matrix operation is a fundamental part of machine learning. Apache Spark provides implementation for distributed and local matrix operation \cite{DBLP:conf/kdd/ZadehMUYPVSSZ16}. 
To translate single-node algorithms to run on a distributed cluster, Spark addresses separating matrix operations from vector operations and run matrix operations on the cluster, 
while keeping vector operations local to the driver.

@@

ND4J \cite{nd4j} has two types of  its own memory management methods, GC to pointer of off-heap NDArray, and MemoryWorkspaces. 
ND4J used off-heap memory to store NDArrats, to provide better performance while working with NDArrays from vative code such as BLAS and CUDA libraries. 
Off-heap means that the memory is allocated outside of the Java heap so that it is not managed by the JVM’s GC. NDArray itself is not tracked by JVM, 
but its pointer is. The Java heap stores pointer to NDArray on off-heap. When a pointer is dereferenced, this pointer can be a target of JVM’s GC and when it is collected, 
the corresponding NDArray will be deallocated. When using MemoryWorkspaces, NDArray lives only within specific workspace scope. 
When NDArray leaves the workspace scope, the memory is deallocated unless explicitly calling method to copy the NDArray out of the scope.

### 2020-05-04 thesis_template/2_RelatedWork/model/os.tex
ready to review

\subsection{Memory and Process in Operating Systems}
\label{sec:os_mem_process}
A process is a subsection of computation job. A process can work on a CPU core. We can divide process as well.
Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
Processes can be represented as tree structure, because a process may create other child processes.
Process has 4 states, new, running, waiting, and ready. 
Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
the waiting process will be pushed tail of ready queue.

@@

\subsection{Copy on Page}
\label{sec:os_copypage}
When a parent process creates child process and if these process shares contents on particular page and modify it, 
only the page which has the context will be copied.

>>>>

\subsection{Memory and Process in Operating Systems}
\label{sec:os_mem_process}
A process is a subsection of computation job. A process can work on a CPU core, we can divide process as well.
Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
Processes can be represented as tree structure, because a process may create other child processes.
Process has 4 states, new, running, waiting, and ready. 
Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
the waiting process will be pushed tail of ready queue.

@@

% \subsection{Copy on Page}
% \label{sec:os_copypage}
% When a parent process creates child process and if these process shares contents on particular page and modify it, 
% only the page which has the context will be copied.
